### 2019-11-28 Mathematical Statistics/ms_ch_04.rmd
ms, ch4
ms, ch4

@@

>>>>

Suppose the _sampling distribution_ of W has a pdf given by $f(x) = \frac{2}{x^2}$, for 1 < x < 2.

Find $P(w < 1.5)$

__Solution__:

### 4.9

Let $X_1, X_2, \ldots, X_{n}$ be a random sample from some distribution and $Y = T(X_1, X_2, \ldots, X_n)$ be a statistic.

@@

__Solution__:

### 4.10

Suppose the heights of boys in a certain large city follow a distribution with mean 48 in. and variance $9^2$.

Use the CLT approximation to estimate the probability that in a random sample of 30 boys, the mean height is more than 51 in.

### 4.11

Let $X_1, X_2, \ldots, X_{36} \sim Bern(.55)$ be independent, and let $\hat{p}$ denote the sample proportion.

Use the CLT approximation with continuity correction to find the probability that $\hat{p} \le 0.5$.

### 4.12

A random sample of size $n = 20$ is drawn from a distribution with mean 6 and variance 10.

Use the CLT approximation to estimate $P(\bar{X} \le 4.6)$.
